Robust Control of a Fluxonium Qubit

### 2020-11-14 paper/3fluxonium.tex
misc updates
removed old dirs

%% S3
\section{QOC on the Fluxonium}
In the following we study
the quantum optimal control problem on the fluxonium qubit.
The fluxonium qubit is a promising building block for superconducting
circuits, and the experimental constraints we encode in the optimization reflect
those of a realistic device. Furthermore, the accurate
two-level approximation of the system Hamiltonian makes it
efficient to perform quantum optimal control on
a classical computer. In the two-level
approximation the system Hamiltonian takes the form
\label{eq:hamiltonian}
\begin{align}
  H/h &= f_{q} \frac{\sigma_{z}}{2} + a(t) \frac{\sigma_{x}}{2}
\end{align}
where $f_{q} = 14$MHz is the qubit frequency at the flux frustration point,
$a$ is the flux drive amplitude, $h$ is Planck's constant, and $\sigma_{x}, \sigma_{y}$
are Pauli matrices. The flux amplitude $a$ is experimentally
realized by modulating the flux 
threading the device. We consider the task of constructing $Z/2$, $Y/2$, and $X/2$
gates for the fluxonium qubit subject to experimental constraints, decoherence, and
systematic errors. We compare the gates we obtain with numerical
methods to the analytically constructed gates reported in
\cite{zhang2020universal} for the same device.

In addition to imposing optimization constraints that
reflect physical limitations of the apparatus, we impose
constraints that improve the experimental realization of the control pulse.
To ensures gates may be concatenated arbitrarily without
inducing AWG ringing due to high-frequency transitions,
we require $a(t = 0) = a(t = t_{N}) = 0$.
Furthermore, we require $\int_{0}^{t_{N}} a(t) dt = 0$. This
constraint ensures the pulse has zero net flux, mitigating
the hysteresis ubiquitous in flux bias lines.
%% TODO: See ref. 28 in Helin paper
We require $-0.5 \textrm{GHz} \le a(t) \le 0.5 \textrm{GHz}$
to ensure the two-level approximation \ref{eq:hamiltonian}
remains valid. Additionally, we require that each gate achieves
the desired state transition $\ket{\psi_{N}} = \ket{\psi_{f}}$.
In addition to these constraints we penalize the norm
of the first and second derivatives of the flux amplitude to
ensure its smoothness, and in doing so mitigate AWG ringing.
The optimization is performed over the second derivative of the flux amplitude
$\frac{d^{2}}{dt^{2}} a$ which is contained in the
augmented control vector. The first derivative
$\frac{d}{dt} a$, proportional $a$, and integral $\int a$
flux amplitude terms
are contained in the augmented state vector. They are obtained from
the second derivative of the flux amplitude by
integration in the dynamics function.
Both the zero net flux and target quantum state constraint
are then handled by ensuring the target augmented state is
reached $x_{N} = x_{f}$.
The equality and inequality constraints on $a$ are handled
with a bound constraint.
%% TODO: probably want to list equations for the constraints

In addition to obeying experimental constraints
and achieving low simulated gate errors, we desire
to make our gates perform well in the presence of decoherence.
Decoherence of the quantum state due to external noise
is typically modeled by two phenomena: longitudinal relaxation and pure dephasing.
They are modeled using their $1/e$ decay times $T_{1}$ and $T_{\phi}$ respectively
(see Appendix).
The main contributions to longitudinal relaxation in our
device are dielectric loss in the capacitor, resistive loss in the inductor,
and Purcell loss. The main contributions to pure dephasing in our
device are $1/f$ flux noise and decay via charge and flux coupling
to the control lines.
Dissipation to the thermal bath via longitudinal
relaxation is an irreversible process
that results in information loss.
Converesely, pure dephasing is a reversible process.
There is a tradeoff between the two decoherence processes. In the case of white
noise the sum of the noise weights $W_{1}$ and $W_{\phi}$
is constant \cite{huang2020engineering}.
Our device achieves its best pure dephasing
protection at the flux frustration point
$T_{2e}(a = 0) \sim 300 \mu\textrm{s}$
where the qubit is first-order insensitive to changes in flux.
It becomes more succeptable to pure dephasing as the flux is tuned away from the flux
frustration point $|a| > 0$. Conversely, longitudinal relaxation is at a minimum
at the flux frustration point $T_{1}(a = 0) = 0.315$ms,
and increases away from the flux frustration point
$T_{1}(a = 0.34 \textrm{GHz}) = 4.3$ms. Given the nature
of the decay processes and the tradeoff, we choose
to maximize the longitudinal relaxation time directly
by tuning the flux amplitude and employ robust control techniques to mitigate
pure dephasing.

>>>>

\section{QOC on the Fluxonium}
In the following we study
the quantum optimal control problem on the fluxonium qubit.
The fluxonium qubit is a promising building block for superconducting
circuits, and the experimental constraints we encode in the optimization reflect
those of a realistic device. Furthermore, the accurate
two-level approximation of the system Hamiltonian makes it
efficient to perform quantum optimal control on
a classical computer. In the two-level
approximation the system Hamiltonian takes the form
\label{eq:hamiltonian}
\begin{align}
  H/h &= f_{q} \frac{\sigma_{z}}{2} + a(t) \frac{\sigma_{x}}{2}
\end{align}
where $f_{q} = 14$MHz is the qubit frequency at the flux frustration point,
$a$ is the flux drive amplitude, $h$ is Planck's constant, and $\sigma_{x}, \sigma_{y}$
are Pauli matrices. The flux amplitude $a$ is experimentally
realized by modulating the flux 
threading the device. We consider the task of constructing $Z/2$, $Y/2$, and $X/2$
gates for the fluxonium qubit subject to experimental constraints, decoherence, and
systematic errors. We compare the gates we obtain with numerical
methods to the analytically constructed gates reported in
\cite{zhang2020universal} for the same device.

In addition to imposing optimization constraints that
reflect physical limitations of the apparatus, we impose
constraints that improve the experimental realization of the control pulse.
To ensures gates may be concatenated arbitrarily without
inducing AWG ringing due to high-frequency transitions,
we require $a(t = 0) = a(t = t_{N}) = 0$.
Furthermore, we require $\int_{0}^{t_{N}} a(t) dt = 0$. This
constraint ensures the pulse has zero net flux, mitigating
the hysteresis ubiquitous in flux bias lines,
\cite{battistel2019fast, krantz2019quantum, zhang2020universal}.
We require $-0.5 \textrm{GHz} \le a(t) \le 0.5 \textrm{GHz}$
to ensure the two-level approximation \ref{eq:hamiltonian}
remains valid. Additionally, we require that each gate achieves
the desired state transition $\ket{\psi_{N}} = \ket{\psi_{f}}$.
In addition to these constraints we penalize the norm
of the first and second derivatives of the flux amplitude to
ensure its smoothness, and in doing so mitigate AWG ringing.
The optimization is performed over the second derivative of the flux amplitude
$\frac{d^{2}}{dt^{2}} a$ which is contained in the
augmented control vector. The first derivative
$\frac{d}{dt} a$, proportional $a$, and integral $\int a$
flux amplitude terms
are contained in the augmented state vector. They are obtained from
the second derivative of the flux amplitude by
integration in the dynamics function.
Both the zero net flux and target quantum state constraint
are then handled by ensuring the target augmented state is
reached $x_{N} = x_{f}$.
The equality and inequality constraints on $a$ are handled
with a bound constraint.
%% TODO: probably want to list equations for the constraints

In addition to obeying experimental constraints
and achieving low simulated gate errors, we desire
to make our gates perform well in the presence of decoherence.
Decoherence of the quantum state due to external noise
is typically modeled by two phenomena: longitudinal relaxation and pure dephasing.
They are modeled using their $1/e$ decay times $T_{1}$ and $T_{\phi}$ respectively.
The main contributions to longitudinal relaxation in our
device are dielectric loss in the capacitor, resistive loss in the inductor,
and Purcell loss. The main contributions to pure dephasing in our
device are $1/f$ flux noise and decay via charge and flux coupling
to the control lines.
Dissipation to the thermal bath via longitudinal
relaxation is an irreversible process
that results in information loss.
Converesely, pure dephasing is a reversible process.
There is a tradeoff between the two decoherence processes. In the case of white
noise the sum of the noise weights $W_{1}$ and $W_{\phi}$
is constant \cite{huang2020engineering}.
Our device achieves its best pure dephasing
protection at the flux frustration point
$T_{2e}(a = 0) \sim 300 \mu\textrm{s}$
where the qubit is first-order insensitive to changes in flux.
It becomes more succeptable to pure dephasing as the flux is tuned away from the flux
frustration point $|a| > 0$. Conversely, longitudinal relaxation is at a minimum
at the flux frustration point $T_{1}(a = 0) = 0.315$ms,
and increases away from the flux frustration point
$T_{1}(a = 0.34 \textrm{GHz}) = 4.3$ms. Given the nature
of the decay processes and the tradeoff, we choose
to maximize the longitudinal relaxation time directly
by tuning the flux amplitude and employ robust control techniques to mitigate
pure dephasing.

### 2020-11-14 paper/5static.tex
removed old dirs

\section{Robustness to Static Parameter Deviations \label{sec:static}}
We have formulated the quantum optimal control
problem as an open loop optimization problem, i.e.
feedback from the experiment is not incorporated in optimization.
However, the device typically deviates from the Hamiltonian we use in optimization,
leading to poor experimental performance. To mitigate
these errors we employ robust control techniques
to make the state evolution insensitive to Hamiltonian
parameter deviations. As an example
we mitigate errors arising from the drift and finite measurement
precision of the qubit frequency $\tilde{f_{q}} = f_{q} \pm \sigma_{f_{q}}$.
We consider three robust control techniques.
The first is the sampling method, which has
been proposed previously in the context of QOC
\cite{rembold2020introduction, reinhold2019controlling, carvalho2020error}. In the
sampling method, multiple states are evolved under distinct deviant dynamics
to capture the effect of parameter deviations. We also
study the unscented sampling method which uses the unscented
transformation to accurately propagate a distribution
representing the uncertainty in an evolving state
due to a parameter deviation.
The unscented transformation was designed for nonlinear Kalman
filtering and is frequently utilized in robust control
\cite{julier2004unscented, lee2013sigma, manchester2016derivative}.
Finally, we propose the derivative method. Derivative
information encoding the sensitivity of the
state trajectory with respect to the deviant parameter
is used to penalize state trajectory deviations.

In the sampling method, sample states evolve under a
Hamiltonian where a parameter is replaced by
a deviant value. We propagate the additional states $\ket{\psi^{\pm}}$ with
deviant values $\lambda^{\pm} = \lambda \pm \sigma_{\lambda}$.
The gate error of each sample state is 
penalized at each knot point
$1 - {\lvert \braket{\psi^{\pm}_{k} | \psi_{f}} \rvert}^{2}$.
Each initial state is used to initialize two
sample states $\ket{\psi^{\pm}}$.
The initial states are chosen so
that their outer products span the operators on the
Hilbert space $\{\ket{0}, \ket{1}, (\ket{0} + i\ket{1}) / \sqrt{2},
(\ket{0} - \ket{1}) / \sqrt{2}\}$ \cite{chow2009randomized}.
For this method the number of states in the augmented state vector
scales as $O(dn^{2})$ because each of $n^{2}$ initial
states is represented by $2d$ samples. $n$ is both the dimension of the Hilbert space
and the size of the state vector. $d$ is the number of deviant parameters.

@@

The strategy of the unscented sampling method is to
propagate an ensemble of sample states (sigma points) which represent a distribution
over every element of the initial state. The distribution
models the uncertainty in each state element arising from the
parameter deviation. The ensemble consists of $2 (n + d)$ states.
Each state in the
ensemble is propagated to the next
knot point using separate deviant dynamics. Then, the mean and covariance of
the propagated ensemble is calculated. New states are sampled from the distribution
given by the calculated statistics for propagation to the next knot point.
This resampling procedure, the unscented transformation, accurately propagates
first and second moments of the distribution and ensures the points
lie on the $\sqrt{n}$\textsuperscript{th}
covariance contour at each knot point. A detailed update procedure is given
in Appendix \ref{appendix:unscented}. Each initial state from the operator basis
is represented with a distribution of $2 (n + d)$ samples. Hence,
the number of states in the augmented state vector scales as $O(n^{3} + dn^{2})$.
The gate error of each sample state is penalized as in the sampling method.

%% TODO: comment on the fact that we can reduce the number of sample states
The derivative method draws on the intuition that
the sensitivity of the state evolution to a parameter
$\lambda$ is encoded in the $l$\textsuperscript{th}-order
derivative of the state with respect to that parameter
$\ket{\partial_{\lambda}^{l} \psi}$. The $m$\textsuperscript{th}-order
derivative method minimizes the norm of the first $m$
state derivatives with a quadratic cost at each knot point
${\lvert \braket{\partial^{l}_{\lambda} \psi | \partial^{l}_{\lambda} \psi}
  \rvert}^{2}$, $l \in \{1, \dots, m\}$.
The state derivatives could be obtained with backwards mode differentiation.
Naive automatic differentiation would compute
the state derivative at all $1, \dots, k - 1$ knot points
to obtain the state derivative at knot point $k$.
For a single state derivative and $N$ knot points this
requires $O(N^2)$ matrix multiplications.
Instead, we forward propagate the state derivatives in the
augmented state vector under coupled dynamics, resulting in
$O(N)$ matrix multiplications. For example, the dynamics
for the 1\textsuperscript{st}-order derivative method are
\begin{align}
  i \hbar \frac{d}{dt} \ket{\psi} &= H \ket{\psi}\\
  i \hbar \frac{d}{dt} \ket{\partial_{\lambda}\psi} &=
  H \ket{\partial_{\lambda} \psi} +
  (\partial_{\lambda} H) \ket{\psi}
\end{align}
Exponential integrators that account for the non-linear
term may be used to efficiently integrate the coupled dynamics,
see Appendix \ref{appendix:derivative}.
For this method $m$ state derivatives are associated with each
initial state from the operator basis.
So, the number of states in the augmented state vector scales as
$O(dmn^{2})$.

@@

%% TODO: fix figure and table referencing
We compare the numerical methods
to an analytically derived $Z/2$ gate, see Figure \ref{fig:static}a. This gate corresponds to
idling at the flux frustration point $a = 0$. The analytic gate
is at the device's speed limit for a $Z/2$ gate $t_{Z/2} = 1 / 4 f_{q}$ and
is simple to derive. Its erroneous rotation angle $2 \pi t_{Z/2} \delta f_{q}$ is linearly sensitive to
the qubit frequency detuning, resulting in a gate error that is quadratically sensitive
to the qubit frequency detutning.
At a one-percent
qubit frequency detuning the analytic gate achieves a gate error $\sim 4.5 \cdot 10^{-5}$,
which is sufficient for quantum error correction, see Figure \ref{fig:static}b.
Although the analytic $Z/2$ gate performs well, it works
only at the gate time $t_{Z/2}$. The ability to perform $Z$ rotations in arbitrary times is critical
for operating multi-qubit experiments in the lab frame.
Each numerical method is able to find solutions at
all gate times above $t_{Z/2}$, but is unable to find solutions at shorter times.
These numerical methods offer an effective scheme for synchronizing
qubits operating at different frequencies $f_{q, i} \neq f_{q, j}$.

%% TOOD: intro sentence
%% TODO: comment on unscented when it is redone
The sampling and unscented sampling methods
converge on qualitatively similar solutions which combine idling periods
with fast ramps to the maximum amplitude. The gate error at a one-percent
detuning from the nominal qubit frequency achieved
by the sampling method does not improve substantially over the
range of gate durations. The unscented sampling method
achieves linear decreases in its gate error with longer gate durations
until half the larmor period $1 / 2 f_{q}$ after which it achieves a consistent
gate error $\sim 3.5 \cdot 10^{-5}$.
The derivative methods converge on qualitatively similar solutions that
use fast traingle pulses at the boundaries and balance time
on either side of the flux-frustration point symmetrically at low amplitudes.
Both methods achieve a super-linear scaling in their gate error as
a function of the gate duration. The gate error for the 1\textsuperscript{st}-order
derivative method approaches zero at the larmor period $1 / f_{q}$, see Figure \ref{fig:static}c.
We believe the 1\textsuperscript{st}-order method outperforms the \textsuperscript{nd}-order
method due to the low contribution of second-order
terms to the gate error in this deviation regime, see Appendix \ref{appendix:derivative}.

>>>>

%% TODO: standardize use of "paramter" vs "system parameter" language
\section{Robustness to Static Parameter Deviations \label{sec:static}}
We have formulated the quantum optimal control
problem as an open loop optimization problem, i.e.
feedback from the experiment is not incorporated in optimization.
However, the device typically deviates from the Hamiltonian we use in optimization,
leading to poor experimental performance. We combat errors
of this form using robust control techniques,
making the state evolution insensitive
to Hamiltonian parameter deviations. As an example
we mitigate errors arising from the drift and finite measurement
precision of the qubit frequency $\tilde{f_{q}} = f_{q} \pm \sigma_{f_{q}}$.
We consider three robust control techniques.
The first is the sampling method, which has
been proposed previously in the context of QOC
\cite{rembold2020introduction, reinhold2019controlling, carvalho2020error}. In the
sampling method, multiple states are evolved under distinct deviant dynamics
to capture the effect of parameter deviations. We also
study the unscented sampling method, which uses the unscented
transformation to accurately propagate a distribution
representing the uncertainty in an evolving state
due to a parameter deviation.
The unscented transformation was designed for nonlinear Kalman
filtering and is frequently utilized in robust control
\cite{julier2004unscented, lee2013sigma, manchester2016derivative}.
Finally, we propose the derivative method. Derivative
information encoding the sensitivity of the
state trajectory with respect to the deviant parameter
is used to penalize state trajectory deviations.

In the sampling method, sample states evolve under a
Hamiltonian where a parameter is replaced by
a deviant value. We propagate the additional states $\ket{\psi^{\pm}}$ with
deviant values $\lambda^{\pm} = \lambda \pm \sigma_{\lambda}$.
The gate error of each sample state is 
penalized at each knot point
$1 - {\lvert \braket{\psi^{\pm}_{k} | \psi_{f}} \rvert}^{2}$.
Each initial state is used to initialize two
sample states $\ket{\psi^{\pm}}$.
The initial states are chosen so
that their outer products span the operators on the
Hilbert space $\{\ket{0}, \ket{1}, (\ket{0} + i\ket{1}) / \sqrt{2},
(\ket{0} - \ket{1}) / \sqrt{2}\}$ \cite{chow2009randomized}.
This is a standard perscription, though knowledge
of the problem can typically be used to reduced the number
of required samples. For this method the number of states in the augmented state vector
scales as $O(dn^{2})$ because each of $n^{2}$ initial
states is represented by $2d$ samples. $n$ is both the dimension of the Hilbert space
and the size of the state vector. $d$ is the number of deviant parameters.

@@

The strategy of the unscented sampling method is to
propagate an ensemble of sample states (sigma points) which represent a distribution
over every element of the initial state. The distribution
models the uncertainty in each state element arising from the
parameter deviation. The ensemble consists of $4n + 2d$ states.
Each state in the
ensemble is propagated to the next
knot point using separate deviant dynamics. Then, the mean and covariance of
the propagated ensemble is calculated. New states are sampled from the distribution
given by the calculated statistics for propagation to the next knot point.
This resampling procedure, the unscented transformation, accurately propagates
first and second moments of the distribution and ensurnes the points
lie on the $\sqrt{2n}$\textsuperscript{th}
covariance contour at each knot point. A detailed update procedure is given
in Appendix \ref{appendix:unscented}. Each initial state from the operator basis
is represented with a distribution of $4n + 2d$ samples. Hence,
the number of states in the augmented state vector scales as $O(n^{3} + dn^{2})$.
The gate error of each sample state is penalized as in the sampling method.

The derivative method draws on the intuition that
the sensitivity of the state evolution to a parameter
$\lambda$ is encoded in the $l$\textsuperscript{th}-order
derivative of the state with respect to that parameter
$\ket{\partial_{\lambda}^{l} \psi}$. The $m$\textsuperscript{th}-order
derivative method minimizes the norm of the first $m$
state derivatives with a quadratic cost at each knot point
${\lvert \braket{\partial^{l}_{\lambda} \psi | \partial^{l}_{\lambda} \psi}
  \rvert}^{2}$, $l \in \{1, \dots, m\}$.
The state derivatives could be obtained with backwards mode differentiation.
Naive automatic differentiation would compute
the state derivative at all $1, \dots, k - 1$ knot points
to obtain the state derivative at knot point $k$.
For a single state derivative and $N$ knot points this
requires $O(N^2)$ matrix multiplications.
Instead, we forward propagate the state derivatives in the
augmented state vector under coupled dynamics, resulting in
$O(N)$ matrix multiplications. For example, the dynamics
for the 1\textsuperscript{st}-order derivative method are
\begin{align}
  i \hbar \frac{d}{dt} \ket{\psi} &= H \ket{\psi}\\
  i \hbar \frac{d}{dt} \ket{\partial_{\lambda}\psi} &=
  H \ket{\partial_{\lambda} \psi} +
  (\partial_{\lambda} H) \ket{\psi}
\end{align}
Exponential integrators that account for the non-linear
term may be used to efficiently integrate the coupled dynamics,
see Appendix \ref{appendix:derivative}.
For this method $m$ state derivatives are associated with each
initial state from the operator basis.
So, the number of states in the augmented state vector scales as
$O(dmn^{2})$.

@@

We compare the numerical methods
to an analytically derived $Z/2$ gate, see Figure \ref{fig:static}a. This gate corresponds to
idling at the flux frustration point $a = 0$. The analytic gate
is at the device's speed limit for a $Z/2$ gate $t_{Z/2} = 1 / 4 f_{q}$ and
is simple to derive. Its erroneous rotation angle $2 \pi t_{Z/2} \delta f_{q}$ is linearly sensitive to
the qubit frequency detuning, resulting in a gate error that is quadratically sensitive
to the qubit frequency detutning.
At a one-percent
qubit frequency detuning the analytic gate achieves a gate error $\sim 4.5 \cdot 10^{-5}$,
which is sufficient for quantum error correction, see Figure \ref{fig:static}b.
Although the analytic $Z/2$ gate performs well, it works
only at the gate time $t_{Z/2}$. The ability to perform $Z$ rotations in arbitrary times is critical
for operating multi-qubit experiments in the lab frame.
Each numerical method is able to find solutions at
all gate times above $t_{Z/2}$, but is unable to find solutions at shorter times.
These numerical methods offer an effective scheme for synchronizing
qubits operating at different frequencies $f_{q, i} \neq f_{q, j}$.

%% TOOD: intro sentence
%% TODO: comment on unscented when it is redone
The sampling and unscented sampling methods
converge on qualitatively similar solutions which combine idling periods
with fast ramps to the maximum amplitude. The gate error at a one-percent
detuning from the nominal qubit frequency achieved
by the sampling method does not improve substantially over the
range of gate durations. The unscented sampling method
achieves linear decreases in its gate error with longer gate durations
until half the larmor period $1 / 2 f_{q}$ after which it achieves a consistent
gate error $\sim 3.5 \cdot 10^{-5}$.
The derivative methods converge on qualitatively similar solutions that
use fast traingle pulses at the boundaries and balance time
on either side of the flux-frustration point symmetrically at low amplitudes.
Both methods achieve a super-linear scaling in their gate error as
a function of the gate duration. The gate error for the 1\textsuperscript{st}-order
derivative method approaches zero at the larmor period $1 / f_{q}$, see Figure \ref{fig:static}c.
We believe the 1\textsuperscript{st}-order method outperforms the 2\textsuperscript{nd}-order
method due to the low contribution of second-order
terms to the gate error in this deviation regime, see Appendix \ref{appendix:derivative}.

### 2020-11-14 paper/a1longitude.tex
removed old dirs

\section{Longitudinal Relaxation}
\label{appendix:longitude}
We comment on the longitudinal relaxation metrics and then give
our procedure for integrating the Lindblad master equation.
The longitudal relaxation probability metric and gate error due to longitudinal
relaxation metric are compared in Table I for the experiment shown in Figure 1c.
The relative performance of the analytic and numerical techniques we study
is similar across the two metrics.

\begin{table}[h!]
  \begin{tabular}{c | c | c | c | c | c | c}
         & $P_{1\textrm{A}}$ & $P_{1\textrm{N}}$ & & GE$_{\textrm{A}}$ & GE$_{\textrm{N}}$ &\\
    Gate & $(10^{-5})$ & $(10^{-5})$ & $P_{1\textrm{A}}/ P_{1\textrm{N}}$ & $(10^{-5})$ &
    $(10^{-5})$ & GE$_{\textrm{A}} / \textrm{GE}_{\textrm{N}}$\\
    \hline
    Z/2 & 5.745 & 1.149 & 5.000 & 1.776 & 0.371 & 4.787\\
    Y/2 & 5.253 & 1.157 & 4.540 & 1.539 & 0.370 & 4.159\\
    X/2 & 16.251 & 2.660 & 6.109 & 5.347 & 0.863 & 6.196\\
  \end{tabular}
  \caption{
    Single gate longitudinal relaxation probability ratios
    and single gate error due to longitudinal relaxation ratios.
    Values are reported for the analytic (A) and numerical (N) techniques
    presented in the main text.
  }
\end{table}

To compute the gate error due to longitudinal relaxation,
we require the final state of the quantum system subject
to longitudinal relaxation. To obtain the final state we employ
the Lindblad master equation. This equation takes the form
\begin{equation}
  \frac{d}{dt} \rho = \frac{-i}{\hbar} [H, \rho]
  + \sum_{i = 1}^{n^{2} - 1} \gamma_{i} (L_{i} \rho L_{i}^{\dagger}
  - \frac{1}{2} \{L_{i}^{\dagger} L_{i}, \rho\})
\end{equation}
Here $\rho = \ket{\psi}\bra{\psi}$ is the density matrix, $n = \textrm{dim}(\mathcal{H})$,
and $[\cdot, \cdot], \{\cdot, \cdot \}$ are the algebraic commutator and anti-commutator.
For longitudinal relaxation $\gamma_{\uparrow} = T_{1, \uparrow}^{-1}$,
$\gamma_{\downarrow} = T_{1, \downarrow}^{-1}$,
$L_{\uparrow} = \sigma^{+}/2$, and
$L_{\downarrow} = \sigma^{-}/2$ where $\sigma^{\pm} = \sigma_{x} \pm i \sigma_{y}$.
Both $T_{1, \uparrow}$ and $T_{1, \downarrow}$ are obtained from the spline shown in Figure 1b.
The $T_{1}$ values in this spline are obtained experimentally by driving the qubit at the desired flux amplitude
and monitoring the resultant decay. For more details consult \cite{zhang2020universal}.

>>>>

\section{Longitudinal Relaxation}
\label{appendix:longitude}
We comment on the longitudinal relaxation metrics and then give
our procedure for integrating the Lindblad master equation.
The longitudal relaxation probability and the gate error due to longitudinal
relaxation metrics are compared in Table \ref{tab:longitude} for the experiment shown in Figure \ref{fig:longitude}c.
The relative performance of the analytic and numerical techniques
is similar across the two metrics.

\begin{table}[h!]
  \begin{tabular}{c | c | c | c | c | c | c}
         & $P_{1\textrm{A}}$ & $P_{1\textrm{N}}$ & & GE$_{\textrm{A}}$ & GE$_{\textrm{N}}$ &\\
    Gate & $(10^{-5})$ & $(10^{-5})$ & $P_{1\textrm{A}}/ P_{1\textrm{N}}$ & $(10^{-5})$ &
    $(10^{-5})$ & GE$_{\textrm{A}} / \textrm{GE}_{\textrm{N}}$\\
    \hline
    Z/2 & 5.745 & 1.149 & 5.000 & 1.776 & 0.371 & 4.787\\
    Y/2 & 5.253 & 1.157 & 4.540 & 1.539 & 0.370 & 4.159\\
    X/2 & 16.251 & 2.660 & 6.109 & 5.347 & 0.863 & 6.196\\
  \end{tabular}
  \caption{
    Single gate longitudinal relaxation probability ratios
    and single gate error due to longitudinal relaxation ratios.
    Values are reported for the analytic (A) and numerical (N) techniques
    presented in the main text.
  }
  \label{tab:longitude}
\end{table}

To compute the gate error due to longitudinal relaxation,
we require the final state of the quantum system subject
to longitudinal relaxation. To obtain the final state we employ
the Lindblad master equation. This equation takes the form
\begin{equation}
  \frac{d}{dt} \rho = \frac{-i}{\hbar} [H, \rho]
  + \sum_{i = 1}^{n^{2} - 1} \gamma_{i} (L_{i} \rho L_{i}^{\dagger}
  - \frac{1}{2} \{L_{i}^{\dagger} L_{i}, \rho\})
\end{equation}
Here $\rho = \ket{\psi}\bra{\psi}$ is the density matrix, $n = \textrm{dim}(\mathcal{H})$,
and $[\cdot, \cdot], \{\cdot, \cdot \}$ are the algebraic commutator and anti-commutator.
For longitudinal relaxation $\gamma_{\uparrow} = T_{1, \uparrow}^{-1}$,
$\gamma_{\downarrow} = T_{1, \downarrow}^{-1}$,
$L_{\uparrow} = \sigma^{+}/2$, and
$L_{\downarrow} = \sigma^{-}/2$ where $\sigma^{\pm} = \sigma_{x} \pm i \sigma_{y}$.
Both $T_{1, \uparrow}$ and $T_{1, \downarrow}$ are obtained from the spline shown in Figure \ref{fig:longitude}b.
The $T_{1}$ values in this spline are obtained experimentally by driving the qubit at the desired flux amplitude
and monitoring the resultant decay. For more details consult \cite{zhang2020universal}.
